Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
deleted repeated word I entered in first idea of pf

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$. Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms terms in $S$ can be contained in $\initial(I)$ since $(1)$ implies that $S$ is a basis.

>>>>

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$. Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
